```{r collect-data, echo = FALSE}
suppressMessages(library('plyr'))
suppressMessages(library('dplyr'))
suppressMessages(library('magrittr'))
suppressMessages(library('formattable'))
suppressMessages(library('knitr'))
suppressMessages(library('sparkline'))

if(!file.exists('data/')) dir.create('data/')

lnk <- 'https://d3c33hcgiwev3.cloudfront.net/_595a8f2c3bcd6e2c185467a9768e641c_Programming-Assignment-1-Data-New.zip?Expires=1461974400&Signature=QMD76O1PvIyB4RkBYDcdwIcZuy9GSYh~cw7iCvTPtZUIdfXr67Bd09DXYs2a3gbfhLjGYWzK3oLHwDrlty~N7Hbcie07X~Sk42G~dFlJ8UIP1a-vt2vTWUDkyZC5LqA5QlRq9VhlHrgljW9-xXkrENO8NxbK2EZd9bZ3ExzW2Po_&Key-Pair-Id=APKAJLTNE6QMUY6HBC5A'
destfile <- 'Programming-Assignment-1-Data-New.zip'

if(!file.exists(paste0('data/', destfile))) {
  download.file(lnk, destfile = paste0('data/', destfile))
}

if(!file.exists(paste0('data/final'))) {
  unzip(paste0('data/', destfile), exdir = 'data/')
}
```

```{r read-files, echo = FALSE, comment = NA, cache = FALSE}
suppressMessages(library('plyr'))
suppressMessages(library('dplyr'))

dat1 <- read.csv2('data/Programming Assignment 1 Data New/ExcelFormattedGISTEMPDataCSV.csv', sep=',') %>% tbl_df %>% mutate_each(funs(as.numeric))

dat2 <- read.csv2('data/Programming Assignment 1 Data New/ExcelFormattedGISTEMPData2CSV.csv', sep=',') %>% tbl_df %>% mutate_each(funs(as.numeric))
```

```{r clear-memory, include = FALSE}
```

```{r unlink, include = FALSE}
## Delete the data folders to save the capacity.
unlink('data/Programming Assignment 1 Data New', recursive = TRUE)
```

```{r data-details, echo = FALSE}
dats <- list(dat1, dat2)

llply(dats, sapply, class)
```

```{r clear-memory, include = FALSE}
```

```{r rm-objs3, include = FALSE}
rm(datafiles, dat1, dat2)
```

```{r clear-memory, include = FALSE}
```

# Data Visulaization


## Zooming Line Chart

  The zooming graph allow you to :
  
  - Click-and-drag to zoom into the elements inside the graph
  - Move the cursor on the points will show you the value
  - You can choose what element(s) to be show on the graph
  - You can download and save the graph in different format through the top corner of right-hand site
  - The graph will be auto zooming to fit the trend if you select/deselect a/some element(s)
  
```{r line-1a, echo = FALSE, results = 'asis', comment = NA, cache = FALSE}
suppressMessages(library('tidyr'))
suppressMessages(library('rCharts'))

td.dat1 <- dats[[1]] %>% gather(Month, Value, Jan:SON) %>% mutate(Year = as.numeric(Year), Month = factor(Month), Value = as.numeric(Value))

## hPlot
L1a <- hPlot(Value ~ Year, data = td.dat1, group = 'Month', type = 'line', size = 'hp', title = 'Zoom with Line Chart 1', subtitle = 'Climate Degree Celsius from Year 1880 to 2015')
L1a$exporting(enabled = T)
L1a$chart(zoomType = "xy", margin = list(left=100, right=100, top=100, bottom=200))
L1a#$show('inline', include_assets = TRUE, cdn = TRUE)
```

  *Climate Degree Celsius from Year 1880 to 2015.*

  From the above graph, the *X Axis* indicates the year and *Y Axis* indicates the degree celsius.
